How to make a delicious pizza

### 2012-12-17 article.tex

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis nec felis eros. Phasellus tristique ultrices mi eget molestie. Nulla turpis augue, adipiscing et dapibus nec, porttitor sed ante. Donec ut arcu augue. Nulla facilisi. Duis tempor nisl enim. Nulla facilisi. Vivamus adipiscing consequat turpis sed dignissim.

\section{Conclusion}

>>>>

* Formal verification
--> Dependent typing of SHP
--> Horn clauses

* Some
Background for Horn clause solving
* Dependent type determination

Definition of Horn clause solving (Informal)

Advantages
* Solution space consideration

* Why do we limit to integer space?

\section{Algorithm Overview}

\subsection{Preliminaries}

$ <num> ::= ... | -2 | -1 | 0 | 1 | 2 | ... $ .
$ <var> ::= x | y | ... $
$ <term> ::= <num> \cdot <var> $
$ <expr> ::=  <term> + <term> + \cdots + <num> >= 0 $
$ <la> ::= <expr>
         | <la> \wedge <la> $
$ <pvar> ::= A | B | ... $
$ <pred> ::= <pvar> ( <var>, <var>, ... ) $
$ <hornTerm> ::= <pvar> | <pred> $
$ <horn> ::= <hornTerm> \wedge <hornTerm> \wedge \cdots \longrightarrow
         <hornTerm> $

* We consider inequalities.
** NOTE: Even we have =, <>, >, <=, we can normalize to >=
         over integer space

\subsection{Generating a tree}

By receiving Horn clauses as an input for the algorithm, we build a
implication tree.

Def <Implication Tree>:

Implication tree is such a tree that every node is labeled by logical
atoms. The label of every node is implied by the conjunction of its
children's label.

* Renaming?

\subsection{Application of Farkas' Lemma}

Correct statement of Farkas' Lemma
Relationship to Craig's Interpolation.

\subsection{Solution space representation}

\section{Extensions}

\subsection{Extension to DAG structure}

* Building graph

* Splitting a graph into tree

* Merging with the same-name predicate conjunctively

\subsection{Linear arithmetics with disjunction}

In the previous section, we assumed that the input inequalities are
conjunctively connected.

* Why do we need this extension? *

We extend our inequalities to include disjunctions in the linear
equations.

$ <la> ::= <expr>
         | <la> \wedge <la>
         | <la> \vee <la> $

* Predicates on the direct path from the leaf with disjunction to the
root are connected by disjunction
* Other predicates are connected by conjunction

* Why do we process LA-disjunction before DAG?
** DAG to LA-Disjunction are invalid???

\subsection{Merging of pred-pred}

* Simplification between clauses

\subsection{General Horn clauses with Loops}

No limitation Horn clause solving

* Merging pred-pred between looped same name

\section{Experiment}
\section{Future Work}
\section{Conclusion}
